%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,bitstream]{moderncv}

% possible options include font size ('10pt', '11pt' and '12pt'),
% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper',
% 'executivepaper' and 'landscape') and font family ('sans' and
% 'roman')

%\renewcommand{\familydefault}{bitstream-charter} % to set the default font;
%use '\sfdefault' for the default sans serif font, '\rmdefault' for
%the default roman one, or any tex font name

\moderncvstyle{classic}
% style options are 'casual' (default), 'classic', 'oldstyle' and
% 'banking'

\moderncvcolor{blue}
% color options 'blue' (default), 'orange', 'green', 'red', 'purple',
% 'grey' and 'black'

\nopagenumbers{}

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.85]{geometry}

\name{Utkarsh}{Gupta}
\address{126 PD Tandon Hostel}{Motilal Nehru National Institute of Technology}{Allahabad - 211004 India}
\email{utkarsh.gupta550@gmail.com}
\mobile{9651755048, 8076566861}
\github{http://khalibartan.github.io/}

\newcommand{\tinygap}{\vspace{7 pt}}
\newcommand{\largegap}{\vspace{10 pt}}

\begin{document}

\makecvtitle

\largegap
\section{Education}

\tinygap
\vbox{\cventry{2014--2018}{Bachelor of Technology}{Motilal Nehru National Institute of Technology Allahabad}{}{}{
Information \& Technology - \textbf{8.74/10 GPA}}}
\vbox{\cventry{2013--14}{Intermediate}{HAL School Korwa, Amethi}{}{}{
CBSE board, Science stream, with Physical Education -\textbf{94\%}}}

\largegap
\section{Experience}
\tinygap
\cventry{April 2016--August 2016}{
  Google Summer of Code Student
}{
   Python Software Foundation (pgmpy) 
}{}{}{
%
  	Implemented Hamiltonian Monte Carlo and No-U-Turn-Sampler (NUTS) sampling
  	algorithm for genrating samples from continuous probablistic models.
  	Proposed design to remove pandas as a strict dependency.
%
}
\tinygap
\cventry{November 2015--Present}{
  Open Source Contributor
}{
    pgmpy:A Python package for Probabilistic Graphical Models 
}{}{}{
%
    Wrote BIF reader, BIF writer and its test suit. Rewrote Joint Probability Distribution class and its test suit. Implemented methods related to I-equivalence. Fixed compatibility issues with python 2.7.x .
%
}
\section{Projects}
\tinygap
\cventry{April 2015}{
 	Pyrag Sports API
}{
    Sports plug-in
}{}{}{
%
    A command line tool cum web API cum browser plug-in to get latest update,
    etc about football and cricket.
    This tool was implemented as part of Hack In the North (IIIT-A) with
    a team of 5 people.
%
}
\tinygap
\cventry{October 2015}{
 	Antidote DM
}{
    A download manger written in Python
}{}{}{
%
    Wrote a GUI software in python that can Download files from web, and with some special features that can search and download from specific sites . Implemented as a part of Softablitz. Our team consisted of 2 people.
%
}
\tinygap
\cventry{October 2015}{
 	Character Classifier and Digit recognizer
}{
    A machine learning script
}{}{}{
%
Implemented a character classifier using scikit-learn SVM implementation.
Implemented a deeplearning 2d-convolutional neural network using keras API for digit recognition, accuracy obtained was 99.1\% (on testing data-set). I was ranked 84th out of 1100+ teams (on kaggle digit recognizer, as of April 2016).
%
}


\largegap
\section{Achievements}
\tinygap
\cventry{October 2015}{
 	Third in Softablitz
}{
    A software development competition in Tech-fest of MNNIT
}{}{}{
%
    Implemented the Antidote DM
%
}
\tinygap
\cventry{October 2015}{
 	Runner up in Logical Rhythm
}{
   Machine learning event in Tech-fest of MNNIT
}{}{}{
%
   Wrote a python script that classifies character in an image using support vector machine. Also wrote a python script for context based search using TF-IDF .
%
}
\section{Skills}
%
\cventry{}{Competent\hspace{0.1cm}}{Python}{}{}{}
\cventry{}{Proficient\hspace{0.4cm}}{C, Git, Vim}{}{}{}
\cventry{}{Familiar\hspace{0.7cm}}{C++, Octave, Java, \LaTeX}{}{}{}
\largegap
\section{Course Work}

\tinygap
\vbox{\cventry{}{Computer Science}{Operating System, Computer Networks,Programming and Data Structures, Algorithms, Cryptography, Object Oriented modelling,Shell scripting, Computer Organization, Automata theory}{}{}{}}
\vbox{\cventry{}{Mathematics}{Linear Algebra, Transform
Calculus, Discrete Mathematics, Numerical Solution to Ordinary
and Partial Differential Equations, Partial Differential Equations, Vector Calculus, Operations Research}{}{}{}}
\vbox{\cventry{}{Electronics}{Analog and Digital electronics, Signals and System, Communication theory}{}{}{}}
\vbox{\cventry{}{Open course-ware}{Introduction to Machine Learning, Heterogeneous Parallel Programming, Finding Hidden Messages in DNA}{}{}{}}
\end{document}